%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:https://www.overleaf.com/project/5c3dcb24970e2c1ceb9b9822
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-red} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Aditya}{Goel}

\email{reachadityagoel@gmail.com}

\linkedin{itsAdityaGoel}

\twitter{itsAdityaGoel}

\mobile{+91-9001791793}

% \quote{} % A quote or statement

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------



% \letterclosing{Sincerely,} % How the letter is closed

% \letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter

\makecvfooter{\today}{Aditya Goel}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
  
%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Bachelors, Masters in Information Technology} % Degree
    {Indian Institute of Information Technology, Allahabad} % Institution
    {Allahabad, India} % Location
    {June 2016 - July 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Merit Scholarship}
        \item{Cummilative GPA : \textbf{9.02}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
%-------------------------------------------------------------------------------



%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Founding Engineer} % Job title
    {Riva Money} % Organization
    {London, Remote} % Location
    {April 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a microservice for \textbf{ingesting Bloomberg Market Data Feed} (Spot and FX forwards for G10 currencies), enabling \textbf{reliable processing of market security updates every 330ms}. Architected components for \textbf{high-throughput data persistence, low-latency querying}, and system resilience. \\
        \textbf{Led end-to-end stakeholder communication} with Bloomberg’s London office.}
        \item {Designed and \textbf{built integrations with a leading identity verification provider} to enable AML/KYB checks during customer onboarding. \textbf{Developed resilient WebClients, scalable webhook handlers, GCS-based secure storage, and asynchronous pipelines} for handling sensitive PII documents with high reliability.}
        \item {\textbf{Self-hosted the Grafana Stack (Loki, Grafana, Tempo, Mimir, and Alloy)} on a Google Cloud GKE cluster using \textbf{GitOps Principles} and Infrastructure as Code. Set up OpenTelemetry agents, structured logging in applications, \textbf{composed Helm charts and supporting Terraform modules} to automate deployment and configuration.}
        \item {Reviewed code across key services including Identity, Transaction Monitoring, Accounts, and Integrated Finance. Contributed to the \textbf{setup of staging and production environments}. Actively participated in \textbf{design and architecture reviews} for all core components of the Riva platform.}
        \item {\textit{\href{}{\color{awesome-red} Tools and Tech Stack:}} \textbf{Java Spring Boot, PostgresQL, Google Cloud, Grafana Stack, Terraform}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer - 2} % Job title
    {Wayfair Inc} % Organization
    {Bengaluru} % Location
    {Dec 2023 - April 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an event driven workflow to \textbf{process 100 million} events daily. Implemented \textbf{error handling and failure management} mechanisms to ensure all events are fully accepted and processed.}
        \item {Led an \textbf{organisation-wide initiative} to identify and rectify root cause of misreported product valuations to the US customs officials. Coordinated with \textbf{lawyers, product managers and engineers from several teams} to fix duty calculation.}
        \item Achieved a \textbf{direct annual gains of \$12MM}, previously incurred as fines and interest due to erroneous customs declarations.
        \item Investigated inconsistencies in items subject to import restrictions that were still being shipped. Developed scripts to identify these items and resolved the root issue.\textbf{ Communicated a \$30MM impact} to the fulfilment team in terms of avoided fines and facilitating the new Canada to US logistics route.
        \item \textbf{Led the development of logistics restriction service} to ensure order fulfillment in compliance with the latest shipping regulations. Oversaw database architecture, high‑level design, and low‑level code implementation
        \item {Developed various Python scripts for activities like data correction, large data ingestion, quarterly reconciliation, and additional business needs.}
        \item {Participated in bug-bash to fix incorrect data on UI portals, improved code structure and overall performance of the system.}
        \item {\textit{\href{}{\color{awesome-red} Tech Stack:}} \textbf{Java, Python, PostgresQL, Google Cloud, GenAI}}
      \end{cvitems}
    }


%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {BlinkIt-Zomato} % Organization
    {Bengaluru} % Location
    {Aug 2021 - Oct 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As a \textbf{product engineer}, I take \textbf{end-to-end ownership} of small and medium features, notably \textbf{BlinkIt-Hyperpure (Zomato)} EDI System, \textbf{Inventory Audit} Workflow, \textbf{Task Auto-Assignment Logic}}
        \item {\textbf{Independently developed} a \textbf{resource allocation engine} for warehouses workforce automation that saved \textbf{75 lakhs per month} in employee cost and \textbf{eliminated 60 hours+} of managerial overhead per day}
        \item {\textbf{Successfully} migrated entire \textbf{inventory pricing} to a new service in a different language, empowering new pricing pipelines and saved several weeks of addition development effort}
        \item{Optimised 10+ nightly jobs to decrease execution time from \textbf{few hours to less than 5 minutes}}
        \item {Contributed in \textbf{cross-team projects} in building \textbf{Multi-Replenishment System}. Shortened the \textbf{New Product On-boarding} and \textbf{Offer Creation} Systems from \textbf{2 weeks to 3 days}}
        \item{Reworked the \textbf{GST computation logic} to accommodate for new product categories and tax changes}
        \item {Implemented \textbf{fail-safe layer} for communication between \textbf{Celery and SQS}. Set up CRON jobs to ensure that 100\% messages are processed despite any initial failure(s).}
        \item {Contributed towards the legal restructuring of \textbf{Grofers to BlinkIt}, worked on invoice sequencing logic and multi-vendor support}
        \item {Responsible for \textbf{Design} (Correctness and Scalability), \textbf{Implementation}, Setting up \textbf{Monitoring and Alerting} (Grafana Dashboards, Sentry, Opsgenie), \textbf{Debug Toolkit} (APIs, queries, RCA tools), \textbf{Performance}, and \textbf{Production Support}}
        % \item {Developed a set of social features on the app aimed at improving the community interaction.}
        \item {\textit{\href{}{\color{awesome-red} Tech Stack:}} \textbf{Golang, Python, Java, MySQL}}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Amazon} % Organization
    {Bangalore} % Location
    {Jan 2021 - July 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Implemented} the design for the \textbf{service migration} of Amazon Pay on \textbf{Amazon.com/Your-Orders} Page.}
        \item {Wrote SJCL contracts (Internal Java Library) to correctly \textbf{navigate complex business conditions} and show the intended data on the page.}
        \item Suggested \textbf{design changes to improve performance}, participated in design reviews, set up new repositories in Amazon Pay, and wrote detailed usage documentation.
        \item {\textbf{Collaborated with overseas sister teams} for code reviews, deployments and contributed to their code base to enable Amazon Pay functionality.}
        \item {\textbf{Successfully migrated 100\% traffic} to the new endpoint for all devices (mobiles, tablets, and PCs), impacting all customers in North America region.}
        \item {\textit{\href{}{\color{awesome-red} Tech Stack:}} \textbf{Horizonte (Java Spring Boot), PHP}}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}



%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Notable Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant | University of Chicago} % Role
    {Inventory Routing Problem With Time Window Optimization} % Event
    {Remote} % Location
    {July 2020 - Jan 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Tasked with reducing the overall cost delivery fleet for replenishing retail stores when the weekly demand is known.}
        \item {Strict time windows at stores, variable heterogeneous fleet, and unknown intermediate stops were amongst the major constraints.}
        \item {\textbf{ Integrated Google Maps API}} to accurately calculate routes and cost.
        \item {\textbf{Developed a Python Library} which computes routes via \textbf{multiple heuristics} and provide insights for each solution.}
        \item Successfully defended the research as a part of Masters' Degree.
        \item {\textit{{\color{awesome-red} Tech Stack:}} Python, Gurobi Optimizers (Mixed Integer Linear Programming)}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Reliance Industries | JIO AI Centre of Excellence} % Role
    {Mixture of Manifold Experts: Large Scale Classification for Genomics} % Event
    {Hyderabad, Remote} % Location
    {Dec 2019 - June 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Built complex mathematical formulations to create affinity networks of data points.}
        \item {Optimised code to run computation for extremely large (genomics) dataset.}
        \item {Integrated the entire process with workflow management tools to schedule jobs.}
        \item {Performance extensive research and experimentation throughout the project.}
        \item {Received several accolades and follow-on internship offers}
        \item {\textit{{\color{awesome-red} Tech Stack:}} Python, Scala, Microsoft Azure}
      \end{cvitems}
    }
\end{cventries}




%---------------------------------------------- End of projects section ----------------------------------------------%


%-------------------------------------------------------------------------------
%	Publications
%-------------------------------------------------------------------------------

\cvsection{Publications}

\begin{cventries}

%---------------------------------------------------------
  \cventry
  {}
  {IEEE} {} {}
  {
    \begin{cvitems}
        \item {P. Shukla, B. Bhandari, \textbf{A. Goel}, et al, \textbf{$"$Fusing Multimodal Human-Robot Communication using Deep Learning$"$}, 2019 International Conference on Electrical, Electronics and Computer Engineering (UPCON), ALIGARH, India, 2019, pp. 1-6, doi: 10.1109/UPCON47278.2019.8980213.}
    \end{cvitems}}
\end{cventries}





% ------------------------


% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)


% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Aditya Goel}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%-------------------------------------------------------------------------------
% \input{resume/summary.tex}
% \input{resume/experience.tex}
% \input{resume/honors.tex}
% \input{resume/presentation.tex}
% \input{resume/writing.tex}
% \input{resume/committees.tex}
% \input{resume/education.tex}
% \input{resume/extracurricular.tex}


%-------------------------------------------------------------------------------
\end{document}
